
\documentclass{book}

\usepackage{
  fancyhdr,    % custom chapter headings
  fullpage,    % reasonable margins
  hyperref,    % hotlinks
  makeidx,     % index
  ebgaramond        % font choice
}

% Don't say "Chapter 3", just "3"
\renewcommand{\chaptername}{}

\makeindex

\begin{document}

\title{Department Chair's Handbook}
\author{Department of Computer Science \\ California State University, Fullerton}
\date{2015 Edition, Revision $\alpha$}
\maketitle

\newpage
\tableofcontents

\chapter{Introduction}

\chapter{Dates \& Calendars}
CSUF Academic Calendar
CSUF Admissions & Records Calendar
Scheduling Office Production Calendar
Academic Senate Calendar

\chapter{Annual Events}
ECS new student orientation
Vannara Touch
give a tour of the building; identify resources in the build such as CASECS, tutoring, labs, etc.
Talk about how to read the schedule, enroll in courses, ugrad handbook, contact the department, placement exams (math, CS, eng), petitioning for courses, math prerequisites, AP exams

ECS Graduate and International Admissions Coordinator

MSE student orientation
MSE Coordinator (James Choi)

\chapter{Scheduling Classes}
start early
entitlements are worked out by Liz and Laura Bazell
Identify courses that match to an adjunct first before contacting them
two courses and the adjunct gets benefits

liz handles contracts, textbooks
sandra handles titanium

\chapter{Meetings}
ECS Chair's Council

\chapter{Office Hours}
In a nutshell, you should hold a minimum of 3 hours of office hours per week. The office hours are typically held in your office but can be held elsewhere. The time and place of the office hours must be posted. A good faith effort must be made to meet your students during office hours and to make any reasonable accommodation for students who cannot.

UPS 230.02 covers faculty office hours. A link to the document is <http://www.fullerton.edu/senate/documents/UPS230.020_Office%20Hours_effec%205-11-12.pdf>.

\chapter{RTP Timelines}
first year prospectus set on timetable set by college UPS 210.000

All the rest of the years governed by calendar at FAR. http://www.fullerton.edu/FAR/
Typically, 2nd year stuff due in Sept. and all the rest due in Oct.
do not share your review with the DPC.
verify the portfolio is complete before signing anything

\chapter{Professional Development}

2015 CSU New Department Chairs Workshop
Friday, October 16
CSU Long Beach Campus
 
The 19th annual CSU New Department Chairs Workshop will be on Friday, October 16, at the CSU Long Beach campus. This is the Friday following the Fall HRO/AVP meetings on October 12-14.  For those of you who are new to your positions, this workshop is targeted to new chairs (newer chairs who didn’t get a chance to attend in their first year are welcome).  We always have sessions featuring experienced chairs sharing their advice and wisdom as well as a session on hot issues from the CBA and additional topics that rotate from year to year.  (We are always on the lookout for suggestions for chairs who would be good presenters as well as topics to include!) We charge the campus a modest fee to cover costs.
Many thanks,
Margaret Merryfield
Assistant Vice Chancellor, Academic Human Resources
CSU Office of the Chancellor
(562) 951-4503
mmerryfield@calstate.edu

\chapter{Business Processes}
\section{Faculty Hiring}
Must identify office space before hiring
\section{D-11}
\section{Moving Expenses}
\section{Travel}
\section{Hardware \& Software Purchases}
Travel expense claims for moving and relocation must be completed and submitted within 30 days of your arrival date.  The travel expense claim for your pre-move house hunting trip (if applicable) must be completed and submitted within 30 days of your return date for that trip.
HR analyst and dept. asc

\section{P Card}




\chapter{Credits and Revision History}

Copyright 2015, Department of Computer Science, California State University, Fullerton.

\chapter{Index}
\printindex

\end{document}
